---
title: "Gun Control CHi Square"
author: "HC"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I am Hope and I am updating this markdown file here.
```{r}
library(tidyverse)

gc_df <- read_csv('gc_df.csv')

```

We are asking: Is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get)?

```{r}
get_guns <- gc_df %>%  
  filter(gender != "NA", make_get_guns != "NA") %>%  
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

get_guns

rownames(get_guns) <- c("Female", "Male")

```


Hi my name is Joslyn, the collaborator, and I'm going to be doing the chi-square test for independence! 

We ask "Is there a sig association btwn sex and opinion on whether guns should be more difficult, easier, or the same to purchase?"


```{r}

# Let's look at the actaul proportions

guns_prop <- prop.table(as.matrix(get_guns), 1) # gives it the margin in which I want to calculate proportions
guns_prop

# Chi-squared test below! 

guns_x2 <- chisq.test(get_guns)
guns_x2

```

"Recommended gov action on gun acccess differed sig btwn male (n= ) and female (n = ) respondents (in-line reference inserted here). Notably, a much higher proportion of female repsondents (57.4%) recommend making it more difficult to get guns, compare to males...."



